---
title: "Homework 8"
author: "Hwasoo Shin"
date: '2019 10 29 '
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(ggplot2)
library(gridExtra)
library(knitr)
```

## Problem 3

We can first read the file and clean up the data.

```{r, results="hide", echo=TRUE, warning=FALSE}
edstat<-read_csv("C:/Users/pc/Desktop/HWASOO/STUDY/StatPackage/Homework8/EdStats_csv/EdStatsData.csv")
summary(edstat)
#We can see that the last column is totally not available. Therefore, we will erase it
dim(edstat)
edstat<-edstat[,-70]
mastered<-edstat #Store the raw data file
checkna<-function(x){
  tf<-sum(is.na(x))<65
  return(tf)
}
idxed<-apply(edstat,1,checkna)
table(idxed) #We can see that the number of rows that have at least one value on year column is 354575.
edstat<-edstat[idxed,]
dim(edstat) #We will only get the data that have valid values.
table(edstat[,1])
edstatmex<-edstat%>%filter(`Country Name`=="Mexico") #Data of Mexico
edstatcan<-edstat%>%filter(`Country Name`=="Canada") #Data of Canada
edstatcom<-rbind(edstatcan,edstatmex) #combine two datasets
```

## Problem 4

```{r, eval=TRUE}
edcomplt<-edstatcom[,c("2000","2010")]
edcomplt2<-edcomplt[which(!is.na(edcomplt[,1])),]
edcomplt3<-edcomplt2[which(!is.na(edcomplt2[,2])),]
colnames(edcomplt3)<-c("Year2000","Year2010")
summary(edcomplt3$Year2010)
edcomplt3<-edcomplt3 %>% filter(Year2010<100)
k<-hist(edcomplt3$Year2010,breaks=50,las=2)
layout(rbind(c(2,2,0),c(1,1,3),c(1,1,3)))
plot(edcomplt3$Year2000,edcomplt3$Year2010)
hist(edcomplt3$Year2000,breaks=50,col=rgb(0.6,0.2,0.3))
barplot(k$counts,horiz=TRUE,col=rgb(0.3,0.8,0.5))
```
We can make a simple histogram and plots to put altogether. To make the plot clean, I selected values which variable "Year2010" is less than 100. We can see there is a high positive correlation between variables "Year2000" and "Year2010". Also, both the variables' values are more concentrated near 0 than other larger values.

## Problem 5

```{r}
p1<-ggplot(data=edcomplt3,aes(x=Year2000,y=Year2010))+geom_point()+theme_light()
p2<-ggplot(data=edcomplt3,aes(x=Year2000))+geom_histogram(fill=rgb(0.8,0.2,0.3,0.8))+xlab("")+theme_classic()
p3<-ggplot(data=edcomplt3,aes(x=Year2010))+geom_histogram(fill=rgb(0.2,0.3,0.9,0.8))+xlab("")+coord_flip()+theme_classic()
grid.arrange(p1,p2,p3,layout_matrix=rbind(c(2,2,NA),c(1,1,3),c(1,1,3)))
```
We can make a same plot with ggplot package.
